Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction

### 2024-03-11 paper/remotesensing-2870812-english.tex
switching png for pdf

\begin{figure}[H]
\vspace{-0.15in}
\includegraphics[width=0.9\columnwidth]{figures/results/fits/physical-fitres.png}
\vspace{-0.1in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
\end{figure}

@@

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/ions-fitres.png}
\vspace{-0.1in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
\end{figure}

@@

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/biochemical-fitres.png}
\vspace{-0.1in}
\caption{Scatter plots (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the final hyperparameter-optimized models for the biochemical targets blue--green algae (phycoerythrin), CDOM, chlorophyll-a, and blue--green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

@@

\vspace{-0.21in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-fitres.png}
\vspace{-0.11in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
\end{figure}

>>>>

\begin{figure}[H]
\vspace{-0.15in}
\includegraphics[width=0.9\columnwidth]{figures/results/fits/physical-fitres.pdf}
\vspace{-0.1in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
\end{figure}

@@

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/ions-fitres.pdf}
\vspace{-0.1in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
\end{figure}

@@

\vspace{-0.15in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/biochemical-fitres.pdf}
\vspace{-0.1in}
\caption{Scatter plots (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the final hyperparameter-optimized models for the biochemical targets blue--green algae (phycoerythrin), CDOM, chlorophyll-a, and blue--green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

@@

\vspace{-0.21in}
\hspace{-6pt}\includegraphics[width=\columnwidth]{figures/results/fits/chemical-fitres.pdf}
\vspace{-0.11in}
\caption{Scatter diagrams (\textbf{left}) and quantile--quantile plots (\textbf{right}) for the hyperparameter-optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
\end{figure}
